Local PCA Shows How Population Structure Differs Along the Genome

### 2016-07-12 writeup/local_pca_paper.tex
updated readme
update

We are indebted to John Pool, Russ Corbett-Detig, Matilde Cordeiro, and Peter Chang 
for assistence with obtaining data and interpreting results
(especially inversion status of \textit{D.~melanogaster} samples).
Thanks also go to Yaniv Brandvain and Barbara Engelhardt for helpful comments 
and for encouraging the project.
\plr{Others?}

@@

\begin{figure}
    \begin{center}
       \includegraphics[width=1\textwidth]{MDS_1D_win100_all_chr_col_by_chr_with_legend}
    \end{center}
    \caption{
        MDS visualization of variation in population structure amongst windows across \emph{all} human autosomes simultaneously.
        The small group of windows with positive MDS values lie around the inversion at 8p23.
        \label{fig:mds1_along_allchr_human}
    }
\end{figure}

@@

\begin{figure}
    \begin{center}
       \includegraphics[width=0.9\textwidth]{FigS_PCA_chr8_outliers_combine}
    \end{center}
    \caption{
        PCA plots comparison for outlier windows and non-outlier windows
        \plr{better caption: which windows?}
        \label{fig:pca_chr8_outliers}
    }
\end{figure}

>>>>

We are indebted to John Pool, Russ Corbett-Detig, Matilde Cordeiro, and Peter Chang 
for assistence with obtaining data and interpreting results
(especially inversion status of \textit{D.~melanogaster} samples).
Thanks also go to Yaniv Brandvain and Barbara Engelhardt for helpful comments 
and for encouraging the project.

@@

\begin{figure}
    \begin{center}
       \includegraphics[width=1\textwidth]{FigS_MDS1D_plot_all_chr_human}
    \end{center}
    \caption{
        MDS visualization of variation in population structure amongst windows across \emph{all} human autosomes simultaneously.
        The small group of windows with positive MDS values lie around the inversion at 8p23.
        \label{fig:mds1_along_allchr_human}
    }
\end{figure}

@@

\begin{figure}
    \begin{center}
       \includegraphics[width=0.9\textwidth]{FigS_PCA_chr8_outliers_combine_update}
    \end{center}
    \caption{
        PCA plots comparison for outlier windows and non-outlier windows.
        \label{fig:pca_chr8_outliers}
    }
\end{figure}
